\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Updated Figure 16 title

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "The $2\\text{-}D$ layout from tSNE applied for the MNIST digit 1 dataset with defualt (hyper-)parameters. We use our *model-in-the-data-space* to assess whether this is an accurate representation of non-linear structure present in $10\\text{-}D$, or if it is misleading. The angle of the digit 1 images varies along this structure. Images at the top-right of the $\\gD{}$ layout show the digit 1 angled more to the right, while those at the bottom-right show the digit 1 angled more to the left."
#| label: fig-tsne-best
#| fig-pos: H
#| out-height: 22%

>>>>

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "The $\\gD{}$ layout from tSNE applied for the MNIST digit 1 dataset with defualt (hyper-)parameters. We use our model in the $10\\text{-}D$ space to assess whether this is an accurate representation of data structure present in $10\\text{-}D$, or if it is misleading. The angle of the digit 1 images varies along this structure. Images at the top-right of the $\\gD{}$ layout show the digit 1 angled more to the right, while those at the bottom-right show the digit 1 angled more to the left."
#| label: fig-tsne-best
#| fig-pos: H
#| out-height: 22%

### 2024-09-06 paper.tex
Updated Figure 16 title

\caption{\label{fig-tsne-best}The \(2\text{-}D\) layout from tSNE
applied for the MNIST digit 1 dataset with defualt (hyper-)parameters.
We use our \emph{model-in-the-data-space} to assess whether this is an
accurate representation of non-linear structure present in
\(10\text{-}D\), or if it is misleading. The angle of the digit 1 images
varies along this structure. Images at the top-right of the \(\gD{}\)
layout show the digit 1 angled more to the right, while those at the
bottom-right show the digit 1 angled more to the left.}

>>>>

\caption{\label{fig-tsne-best}The \(\gD{}\) layout from tSNE applied for
the MNIST digit 1 dataset with defualt (hyper-)parameters. We use our
model in the \(10\text{-}D\) space to assess whether this is an accurate
representation of data structure present in \(10\text{-}D\), or if it is
misleading. The angle of the digit 1 images varies along this structure.
Images at the top-right of the \(\gD{}\) layout show the digit 1 angled
more to the right, while those at the bottom-right show the digit 1
angled more to the left.}
